Eye-tracking

### 2019-02-11 ngrams/prelim_ngrams.Rmd
ngram computation

```{r corpora}
prov_utterances <- get_utterances(corpus = "Providence") %>% 
  filter(speaker_role == "Target_Child") %>%
  mutate(words = stem)

@@

zhou_utterances <- get_utterances(corpus = "ZhouDinner") %>%
  filter(speaker_role == "Target_Child") %>%
  rename(words = stem)

@@

 tokens <- utterances %>%
  mutate(length = str_count(words, pattern = "[ +]+") + 1) %>%
  filter(length == target_length) %>%
  mutate(utterance_id = 1:n()) %>%
  unnest_tokens(ngrams, words, token = "ngrams", n = N) %>%
  group_by(utterance_id) %>%
  mutate(gram_order = 1:n()) %>%
  group_by(gram_order, ngrams) %>%
  filter(gram_order <= target_length - (N-1))

 tokens %>%
  summarise(n = n()) %>%
  tidyboot(summary_function = function(x) x %>% 
        summarise(entropy = entropy(n, unit = "log2")),
       statistics_functions = function(x) x %>%
       summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
  mutate(length = target_length)
}
```

>>>>

```{r corpora}
prov_utterances <- get_utterances(corpus = "Providence") %>% 
  filter(speaker_role != "Target_Child") %>%
  mutate(words = stem)

@@

zhou_utterances <- get_utterances(corpus = "ZhouDinner") %>%
  filter(speaker_role != "Target_Child") %>%
  rename(words = stem)

@@

  tokens <- utterances %>%
    mutate(length = str_count(words, pattern = "[ +]+") + 1) %>%
    filter(length == target_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, words, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n())

  lags <- expand.grid(lag_n = 1:(N-1), 
                      utterance_id = unique(tokens$utterance_id))

  grams <- tokens %>%
    left_join(lags, by = "utterance_id") %>%
    group_by(utterance_id, lag_n) %>%
    arrange(utterance_id, lag_n, word_order) %>%
    mutate(lag = lag(word, n = first(lag_n))) %>%
    group_by(utterance_id, word_order, word) %>%
    summarise(gram = paste(lag, collapse = " ")) %>%
    summarise(gram = paste(gram, word, collapse = " ")) %>%
    filter(word_order >= N) %>%
    rename(gram_order = word_order) %>%
    group_by(gram_order, gram)

 grams %>%
  summarise(n = n()) %>%
  tidyboot(summary_function = function(x) x %>% 
        summarise(entropy = entropy(n, unit = "log2")),
       statistics_functions = function(x) x %>%
       summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
  mutate(length = target_length)
}
```
